Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-10-18 README.rmd
repository organization

### Supplementary figures

@@

@@

**Table 3: Daily mean dietary intake of macro nutrients during each training day per supplement leg.** Glu = glucose,Plac = placebo. Training day 1-training day 12 are combined pairwise to day 1-6: Day 1 = training day 1/2, Day 2 = training day 3/4, Day 3 = training day 5/6, Day 4 = training day 7/8, Day 5 = training day 9/10, Day 6 = training day 11/12. Values are mean ± standard deviation. P = difference between Glu and Plac. Glucose n = 12, placebo n = 12. Day 6: Glu = 11, Plac = 11.
```{r nutrition table, echo=FALSE, message=FALSE, warning=FALSE}
### Nutrition data table

@@

>>>>

## Supplementary figures

@@

#### Macronutrients

@@

**Table 3: Daily mean dietary intake of macro nutrients during each training day per supplement leg.** Glu = glucose,Plac = placebo. Training day 1-training day 12 are combined pairwise to day 1-6: Day 1 = training day 1/2, Day 2 = training day 3/4, Day 3 = training day 5/6, Day 4 = training day 7/8, Day 5 = training day 9/10, Day 6 = training day 11/12. Values are mean ± standard deviation. P = difference between Glu and Plac. Glucose n = 12, placebo n = 12. Day 6: Glu = 11, Plac = 11.

```{r nutrition table, echo=FALSE, message=FALSE, warning=FALSE}
### Nutrition data table

@@

#### Training volume

```{r total session volume figure, echo=FALSE, message=FALSE, warning=FALSE}

### Total session volume change

# Absolute changes are presented as mean change ± SD per supplement

# Packages
library(readxl);library(tidyverse);library(knitr);library(lme4);library(broom);library(emmeans)

# Data
tot.vol <- read_excel("./data/training/ribose_volume.xlsx", na = "NA") %>%
  select(subject, timepoint, tot.volume, supplement)

## Handling the data by creating a new factor called time from timepoint. This factor combines any observation at T1 and T2 to baseline, etc. 
# The code also sorts the order of the factor time, from baseline to session 6, using time = factor(time, levels c()), and sets placebo to be compared to 
# glucose via supplement = factor(supplement, levels = c()).

tot.volh <- tot.vol %>%
  mutate(time = if_else(timepoint %in% c("T1", "T2"),
                        "baseline",
                        if_else(timepoint %in% c("D3", "D4"),
                                "session2",
                                if_else(timepoint %in% c("D5", "D6"),
                                        "session3",
                                        if_else(timepoint %in% c("D7", "D8"),
                                                "session4",
                                                if_else(timepoint %in% c("D9", "D10"),
                                                        "session5",
                                                        if_else(timepoint %in% c("T3", "T4"),
                                                                "session6", timepoint))))))) %>%
  mutate(time = factor(time, levels = c("baseline", "session1", "session2", "session3", "session4", "session5", "session6")),
         supplement = factor(supplement, levels = c("placebo", "glucose")))

## Baseline analysis - comparison of the two legs
# A baseline analysis comparing training volume at baseline sessions between the two legs via a paired t.test, and providing a summary of mean training
# volume and sd

base.vol <- tot.volh %>%
  filter(time == "baseline") %>%
  select(subject, time, supplement, tot.volume) %>%
  group_by(supplement) %>%
  pivot_wider(names_from = supplement,
              values_from = tot.volume)

vol.ttest <- t.test(base.vol$glucose, base.vol$placebo, paired = TRUE)

vol.summary <- tot.volh %>%
  filter(time == "baseline") %>%
  select(subject, time, supplement, tot.volume) %>%
  group_by(supplement) %>%
  mutate(m = mean(tot.volume),
         s = sd(tot.volume))

## Absolute data - summarising mean and SD for barplot
# Mean and SD are calculated from absolute (kg) total volume, creating a basis for a barplot.

vol.exp <- tot.volh %>%
  select(subject, supplement, time, tot.volume) %>% 
  group_by(supplement, time) %>%
  summarise(mean.vol = mean(tot.volume),
            sd.vol = sd(tot.volume))

totvol.barplot <- ggplot(vol.exp, aes(fill = supplement, y = mean.vol, x = time)) +
  #annotate("text", x = c("session4", "session5", "session6"),
   #        y = c(8500, 8500, 8700), label = "†") +
  geom_bar(position = "dodge", stat = "identity") +
  geom_errorbar(aes( ymin = mean.vol - sd.vol, ymax = mean.vol + sd.vol),
                width = 0.2,
                position = position_dodge(width = 1)) +
  labs(x = "", y = "Training volume \n(kg)\n", fill = "Supplement") +
  scale_x_discrete(labels=c("baseline" = "Baseline", "session2" = "Session 2", "session3" = "Session 3",
                            "session4" = "Session 4", "session5" = "Session 5", 
                            "session6" = "Session")) +
  #scale_y_continuous(limits = c(0, 10), breaks = c(0, 1, 2, 3, 4, 5, 6,
  #                                                7, 8, 9, 10),
  #                 expand = expand_scale(0)) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 7, angle = 45, hjust = 1))

totvol.barplot

**Figure 5:** Changes in total training session volume from baseline until resistance exercise session 6 (training day 11 and 12). Baseline = Training day 1/2, Session 2 = Training day 3/4, Session 3 = Training day 5/6, Session 4 = Training day 7/8, Session 5 = Training day 9/10, Session 6 = Training day 11/12. Values are mean kg ± standard deviation.
